quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-09-17 paper-quollr.Rmd
Updated with new implementation

scurve_model_obj <- fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 15, 
  q = 0.1, 
  hd_thresh = 1)

@@

scurve_umap_model_vis <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from,
                         lineTo = tr_from_to_df_scurve$to,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")

scurve_umap_model_vis_n <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from,
                         lineTo = tr_from_to_df_scurve$to,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "300px", height = "300px")

@@

```{r, echo=TRUE, eval=FALSE}
fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 15, 
  q = 0.1, 
  hd_thresh = 1)
```

@@

```{r, echo=TRUE}
bin_configs <- calc_bins_y(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1)

@@

```{r, echo=TRUE}
hb_obj <- hex_binning(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1)
```

@@

```{r, echo=TRUE}
all_centroids_df <- gen_centroids(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1
  )

@@

```{r, echo=TRUE}
find_low_dens_hex(
  model_2d = df_bin_centroids, 
  b1 = 15, 
  md_thresh = 0.05
)

@@

limb_highd_vis <- langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = trimesh_data_limb$from,
                         lineTo = trimesh_data_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")
```

@@

limb_highd_vis_best <- langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = trimesh_data_limb$from,
                         lineTo = trimesh_data_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")
```

>>>>

scurve_model_obj <- fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 15, 
  q = 0.1, 
  hd_thresh = 0)

@@

scurve_umap_model_vis <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from_reindexed,
                         lineTo = tr_from_to_df_scurve$to_reindexed,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")

scurve_umap_model_vis_n <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from_reindexed,
                         lineTo = tr_from_to_df_scurve$to_reindexed,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "300px", height = "300px")

@@

```{r, echo=TRUE, eval=FALSE}
fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 25, 
  q = 0.1, 
  hd_thresh = 1)
```

@@

```{r, echo=TRUE}
bin_configs <- calc_bins_y(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 25, 
  q = 0.1)

@@

```{r, echo=TRUE}
hb_obj <- hex_binning(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 25, 
  q = 0.1)
```

@@

```{r, echo=TRUE}
all_centroids_df <- gen_centroids(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 25, 
  q = 0.1
  )

@@

```{r, echo=TRUE}
find_low_dens_hex(
  model_2d = df_bin_centroids, 
  b1 = 25, 
  md_thresh = 0.05
)

@@

limb_highd_vis <- langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = trimesh_data_limb$from_reindexed,
                         lineTo = trimesh_data_limb$to_reindexed,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")
```

@@

limb_highd_vis_best <- langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = trimesh_data_limb$from_reindexed,
                         lineTo = trimesh_data_limb$to_reindexed,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")
```

### 2025-09-17 paper-quollr.tex
Updated with new implementation

\begin{verbatim}
fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 15, 
  q = 0.1, 
  hd_thresh = 1)
\end{verbatim}

@@

\begin{verbatim}
bin_configs <- calc_bins_y(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1)

@@

\begin{verbatim}
> $b2
> [1] 20
> 
> $a1
> [1] 0.0834108
> 
> $a2
> [1] 0.07223587
\end{verbatim}

@@

\begin{verbatim}
hb_obj <- hex_binning(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1)
\end{verbatim}

@@

\begin{verbatim}
all_centroids_df <- gen_centroids(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1
  )

@@

\begin{verbatim}
> # A tibble: 300 x 3
>        h     c_x    c_y
>    <int>   <dbl>  <dbl>
>  1     1 -0.1    -0.116
>  2     2 -0.0166 -0.116
>  3     3  0.0668 -0.116
>  4     4  0.150  -0.116
>  5     5  0.234  -0.116
>  6     6  0.317  -0.116
>  7     7  0.400  -0.116
>  8     8  0.484  -0.116
>  9     9  0.567  -0.116
> 10    10  0.651  -0.116
> # i 290 more rows
\end{verbatim}

@@

\begin{verbatim}
>   h          x           y
> 1 1 -0.1000000 -0.06752289
> 2 1 -0.1417054 -0.09160152
> 3 1 -0.1417054 -0.13975877
> 4 1 -0.1000000 -0.16383739
> 5 1 -0.0582946 -0.13975877
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 4
>    emb1  emb2    ID     h
>   <dbl> <dbl> <int> <int>
> 1 0.277 0.913     1   216
> 2 0.697 0.538     2   145
> 3 0.779 0.399     3   116
> 4 0.173 0.953     4   229
> 5 0.218 0.983     5   229
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 3
>       h   n_h   w_h
>   <int> <int> <dbl>
> 1    34     1 0.001
> 2    35    10 0.01 
> 3    36     8 0.008
> 4    37     8 0.008
> 5    38     2 0.002
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 2
>       h pts_list  
>   <int> <list>    
> 1    34 <int [1]> 
> 2    35 <int [10]>
> 3    36 <int [8]> 
> 4    37 <int [8]> 
> 5    38 <int [2]>
\end{verbatim}

@@

\begin{verbatim}
>   h        c_x        c_y n_h w_h
> 1 1 -0.1000000 -0.1156801   0   0
> 2 2 -0.0165892 -0.1156801   0   0
> 3 3  0.0668216 -0.1156801   0   0
> 4 4  0.1502324 -0.1156801   0   0
> 5 5  0.2336432 -0.1156801   0   0
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 8
>    from    to  x_from  y_from    x_to    y_to from_count to_count
>   <int> <int>   <dbl>   <dbl>   <dbl>   <dbl>      <dbl>    <dbl>
> 1     1     2 -0.1    -0.116  -0.0166 -0.116           0        0
> 2    16    17 -0.0583 -0.0434  0.0251 -0.0434          0        0
> 3    16    32 -0.0583 -0.0434 -0.0166  0.0288          0        0
> 4     3    17  0.0668 -0.116   0.0251 -0.0434          0        0
> 5    32    33 -0.0166  0.0288  0.0668  0.0288          0        0
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 10
>    from    to  x_from  y_from    x_to    y_to from_count to_count from_reindexed
>   <int> <int>   <dbl>   <dbl>   <dbl>   <dbl>      <dbl>    <dbl>          <int>
> 1     1     2 -0.1    -0.116  -0.0166 -0.116           0        0              1
> 2    16    17 -0.0583 -0.0434  0.0251 -0.0434          0        0             16
> 3    16    32 -0.0583 -0.0434 -0.0166  0.0288          0        0             16
> 4     3    17  0.0668 -0.116   0.0251 -0.0434          0        0              3
> 5    32    33 -0.0166  0.0288  0.0668  0.0288          0        0             32
> # i 1 more variable: to_reindexed <int>
\end{verbatim}

@@

\begin{verbatim}
find_low_dens_hex(
  model_2d = df_bin_centroids, 
  b1 = 15, 
  md_thresh = 0.05
)
\end{verbatim}

\begin{verbatim}
>   [1]   1   2   3   4   5   6   7   8   9  10  11  12  13  14  15  16  17  18
>  [19]  19  20  21  22  23  24  25  26  27  28  29  30  31  32  33  34  35  36
>  [37]  37  38  39  40  41  42  43  44  45  46  47  48  49  50  51  52  53  54
>  [55]  55  56  57  58  59  60  61  62  63  64  65  66  67  68  69  70  71  72
>  [73]  73  74  75  76  77  78  79  80  81  82  83  84  85  86  87  88  89  90
>  [91]  91  92  93  94  95  96  97  98  99 100 101 102 103 104 105 106 107 108
> [109] 109 110 111 112 113 114 115 116 117 118 119 120 121 122 123 124 125 126
> [127] 127 128 129 130 131 132 133 134 135 136 137 138 139 140 141 142 143 144
> [145] 145 146 147 148 149 150 151 152 153 154 155 156 157 158 159 160 161 162
> [163] 163 164 165 166 167 168 169 170 171 172 173 174 175 176 177 178 179 180
> [181] 181 182 183 184 185 186 187 188 189 190 191 192 193 194 195 196 197 198
> [199] 199 200 201 202 203 204 205 206 207 208 209 210 211 212 213 214 215 216
> [217] 217 218 219 220 221 222 223 224 225 226 227 228 229 230 231 232 233 234
> [235] 235 236 237 238 239 240 241 242 243 244 245 246 247 248 249 250 251 252
> [253] 253 254 255 256 257 258 259 260 261 262 263 264 265 266 267 268 269 270
> [271] 271 272 273 274 275 276 277 278 279 280 281 282 283 284 285 286 287 288
> [289] 289 290 291 292 293 294 295 296 297 298 299 300
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 8
>       h     x1     x2    x3         x4        x5      x6         x7
>   <int>  <dbl>  <dbl> <dbl>      <dbl>     <dbl>   <dbl>      <dbl>
> 1    34 0.958  0.0854  1.29  0.00265    0.0171    0.0876 -0.00249  
> 2    35 0.818  0.116   1.56  0.00184    0.00361  -0.0318 -0.00377  
> 3    36 0.544  0.111   1.83 -0.00341   -0.000303  0.0196  0.0000704
> 4    37 0.279  0.128   1.95  0.0000880  0.00104  -0.0276 -0.000227 
> 5    38 0.0567 0.119   2.00  0.00733    0.00238   0.0833 -0.00166
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 4
>   pred_emb_1 pred_emb_2    ID pred_h
>        <dbl>      <dbl> <int>  <int>
> 1      0.234      0.896     1    215
> 2      0.692      0.534     2    145
> 3      0.776      0.390     3    116
> 4      0.192      0.968     4    229
> 5      0.192      0.968     5    229
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 1 x 2
>   Error  RMSE
>   <dbl> <dbl>
> 1  273. 0.163
\end{verbatim}

>>>>

\begin{verbatim}
fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 25, 
  q = 0.1, 
  hd_thresh = 1)
\end{verbatim}

@@

\begin{verbatim}
bin_configs <- calc_bins_y(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 25, 
  q = 0.1)

@@

\begin{verbatim}
> $b2
> [1] 33
> 
> $a1
> [1] 0.04952516
> 
> $a2
> [1] 0.04289005
\end{verbatim}

@@

\begin{verbatim}
hb_obj <- hex_binning(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 25, 
  q = 0.1)
\end{verbatim}

@@

\begin{verbatim}
all_centroids_df <- gen_centroids(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 25, 
  q = 0.1
  )

@@

\begin{verbatim}
> # A tibble: 825 x 3
>        h       c_x    c_y
>    <int>     <dbl>  <dbl>
>  1     1 -0.1      -0.116
>  2     2 -0.0505   -0.116
>  3     3 -0.000950 -0.116
>  4     4  0.0486   -0.116
>  5     5  0.0981   -0.116
>  6     6  0.148    -0.116
>  7     7  0.197    -0.116
>  8     8  0.247    -0.116
>  9     9  0.296    -0.116
> 10    10  0.346    -0.116
> # i 815 more rows
\end{verbatim}

@@

\begin{verbatim}
>   h           x           y
> 1 1 -0.10000000 -0.08708678
> 2 1 -0.12476258 -0.10138346
> 3 1 -0.12476258 -0.12997683
> 4 1 -0.10000000 -0.14427351
> 5 1 -0.07523742 -0.12997683
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 4
>    emb1  emb2    ID     h
>   <dbl> <dbl> <int> <int>
> 1 0.277 0.913     1   609
> 2 0.697 0.538     2   392
> 3 0.779 0.399     3   319
> 4 0.173 0.953     4   631
> 5 0.218 0.983     5   657
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 3
>       h   n_h   w_h
>   <int> <int> <dbl>
> 1    82     1 0.001
> 2    83     4 0.004
> 3    84     1 0.001
> 4    85     3 0.003
> 5    86     1 0.001
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 2
>       h pts_list 
>   <int> <list>   
> 1    82 <int [1]>
> 2    83 <int [4]>
> 3    84 <int [1]>
> 4    85 <int [3]>
> 5    86 <int [1]>
\end{verbatim}

@@

\begin{verbatim}
>   h           c_x        c_y n_h w_h
> 1 1 -0.1000000000 -0.1156801   0   0
> 2 2 -0.0504748374 -0.1156801   0   0
> 3 3 -0.0009496749 -0.1156801   0   0
> 4 4  0.0485754877 -0.1156801   0   0
> 5 5  0.0981006503 -0.1156801   0   0
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 8
>    from    to    x_from  y_from    x_to    y_to from_count to_count
>   <int> <int>     <dbl>   <dbl>   <dbl>   <dbl>      <dbl>    <dbl>
> 1     1     2 -0.1      -0.116  -0.0505 -0.116           0        0
> 2    26    27 -0.0752   -0.0728 -0.0257 -0.0728          0        0
> 3     3    27 -0.000950 -0.116  -0.0257 -0.0728          0        0
> 4    26    52 -0.0752   -0.0728 -0.0505 -0.0299          0        0
> 5    27    28 -0.0257   -0.0728  0.0238 -0.0728          0        0
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 10
>    from    to    x_from  y_from    x_to    y_to from_count to_count
>   <int> <int>     <dbl>   <dbl>   <dbl>   <dbl>      <dbl>    <dbl>
> 1     1     2 -0.1      -0.116  -0.0505 -0.116           0        0
> 2    26    27 -0.0752   -0.0728 -0.0257 -0.0728          0        0
> 3     3    27 -0.000950 -0.116  -0.0257 -0.0728          0        0
> 4    26    52 -0.0752   -0.0728 -0.0505 -0.0299          0        0
> 5    27    28 -0.0257   -0.0728  0.0238 -0.0728          0        0
> # i 2 more variables: from_reindexed <int>, to_reindexed <int>
\end{verbatim}

@@

\begin{verbatim}
find_low_dens_hex(
  model_2d = df_bin_centroids, 
  b1 = 25, 
  md_thresh = 0.05
)
\end{verbatim}

\begin{verbatim}
>   [1]   1   2   3   4   5   6   7   8   9  10  11  12  13  14  15  16  17  18
>  [19]  19  20  21  22  23  24  25  26  27  28  29  30  31  32  33  34  35  36
>  [37]  37  38  39  40  41  42  43  44  45  46  47  48  49  50  51  52  53  54
>  [55]  55  56  57  58  59  60  61  62  63  64  65  66  67  68  69  70  71  72
>  [73]  73  74  75  76  77  78  79  80  81  82  83  84  85  86  87  88  89  90
>  [91]  91  92  93  94  95  96  97  98  99 100 101 102 103 104 105 106 107 108
> [109] 109 110 111 112 113 114 115 116 117 118 119 120 121 122 123 124 125 126
> [127] 127 128 129 130 131 132 133 134 135 136 137 138 139 140 141 142 143 144
> [145] 145 146 147 148 149 150 151 152 153 154 155 156 157 158 159 160 161 162
> [163] 163 164 165 166 167 168 169 170 171 172 173 174 175 176 177 178 179 180
> [181] 181 182 183 184 185 186 187 188 189 190 191 192 193 194 195 196 197 198
> [199] 199 200 201 202 203 204 205 206 207 208 209 210 211 212 213 214 215 216
> [217] 217 218 219 220 221 222 223 224 225 226 227 228 229 230 231 232 233 234
> [235] 235 236 237 238 239 240 241 242 243 244 245 246 247 248 249 250 251 252
> [253] 253 254 255 256 257 258 259 260 261 262 263 264 265 266 267 268 269 270
> [271] 271 272 273 274 275 276 277 278 279 280 281 282 283 284 285 286 287 288
> [289] 289 290 291 292 293 294 295 296 297 298 299 300 301 302 303 304 305 306
> [307] 307 308 309 310 311 312 313 314 315 316 317 318 319 320 321 322 323 324
> [325] 325 326 327 328 329 330 331 332 333 334 335 336 337 338 339 340 341 342
> [343] 343 344 345 346 347 348 349 350 351 352 353 354 355 356 357 358 359 360
> [361] 361 362 363 364 365 366 367 368 369 370 371 372 373 374 375 376 377 378
> [379] 379 380 381 382 383 384 385 386 387 388 389 390 391 392 393 394 395 396
> [397] 397 398 399 400 401 402 403 404 405 406 407 408 409 410 411 412 413 414
> [415] 415 416 417 418 419 420 421 422 423 424 425 426 427 428 429 430 431 432
> [433] 433 434 435 436 437 438 439 440 441 442 443 444 445 446 447 448 449 450
> [451] 451 452 453 454 455 456 457 458 459 460 461 462 463 464 465 466 467 468
> [469] 469 470 471 472 473 474 475 476 477 478 479 480 481 482 483 484 485 486
> [487] 487 488 489 490 491 492 493 494 495 496 497 498 499 500 501 502 503 504
> [505] 505 506 507 508 509 510 511 512 513 514 515 516 517 518 519 520 521 522
> [523] 523 524 525 526 527 528 529 530 531 532 533 534 535 536 537 538 539 540
> [541] 541 542 543 544 545 546 547 548 549 550 551 552 553 554 555 556 557 558
> [559] 559 560 561 562 563 564 565 566 567 568 569 570 571 572 573 574 575 576
> [577] 577 578 579 580 581 582 583 584 585 586 587 588 589 590 591 592 593 594
> [595] 595 596 597 598 599 600 601 602 603 604 605 606 607 608 609 610 611 612
> [613] 613 614 615 616 617 618 619 620 621 622 623 624 625 626 627 628 629 630
> [631] 631 632 633 634 635 636 637 638 639 640 641 642 643 644 645 646 647 648
> [649] 649 650 651 652 653 654 655 656 657 658 659 660 661 662 663 664 665 666
> [667] 667 668 669 670 671 672 673 674 675 676 677 678 679 680 681 682 683 684
> [685] 685 686 687 688 689 690 691 692 693 694 695 696 697 698 699 700 701 702
> [703] 703 704 705 706 707 708 709 710 711 712 713 714 715 716 717 718 719 720
> [721] 721 722 723 724 725 726 727 728 729 730 731 732 733 734 735 736 737 738
> [739] 739 740 741 742 743 744 745 746 747 748 749 750 751 752 753 754 755 756
> [757] 757 758 759 760 761 762 763 764 765 766 767 768 769 770 771 772 773 774
> [775] 775 776 777 778 779 780 781 782 783 784 785 786 787 788 789 790 791 792
> [793] 793 794 795 796 797 798 799 800 801 802 803 804 805 806 807 808 809 810
> [811] 811 812 813 814 815 816 817 818 819 820 821 822 823 824 825
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 8
>       h    x1     x2    x3       x4       x5      x6       x7
>   <int> <dbl>  <dbl> <dbl>    <dbl>    <dbl>   <dbl>    <dbl>
> 1    82 0.888 0.102   1.46  0.0145  -0.0118   0.0303 -0.00707
> 2    83 0.744 0.123   1.66 -0.00950  0.00499 -0.0208 -0.00425
> 3    84 0.591 0.0447  1.81 -0.0168   0.0173  -0.0485 -0.00112
> 4    85 0.371 0.0937  1.93 -0.00109  0.00840  0.0268 -0.00286
> 5    86 0.255 0.0447  1.97 -0.00862 -0.00733 -0.0826  0.00229
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 4
>   pred_emb_1 pred_emb_2    ID pred_h
>        <dbl>      <dbl> <int>  <int>
> 1     NA         NA         1    609
> 2      0.717      0.528     2    392
> 3      0.791      0.399     3    319
> 4      0.172      0.957     4    631
> 5      0.197      0.999     5    657
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 1 x 2
>   Error  RMSE
>   <dbl> <dbl>
> 1  265. 0.157
\end{verbatim}
